### 2023-03-08 manuscript.tex
Updating authorship order in accordance with #309 [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4367208550

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8ffc29ead8fe50fa37fb68dc41d9fc3c10f316fc}{SORTEE-Github-Hackathon/manuscript@8ffc29e}
on March 8, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1ca2ca79ea1ca4ca324b13f577b7bd2b52a8a8eb}{SORTEE-Github-Hackathon/manuscript@1ca2ca7}
on March 8, 2023.
